%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Junior Software Developer} % Job title
    { Applied Virtual Simulation} % Organization
    {Broadmeadow, NSW} % Location
    {Jan 2023 to Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item Following internship, started a casual position while finishing studies
         \item Developed and configured content to support LSCore 2.0, An updated high fidelity military simulation for the Australian army.
         \begin{itemize}
             \item Contributed to the development of Lua based unit behaviour scripts
             \item Contributed to the development of Electron based Vue configuration tool
             \item Wrote and Researched high quality design documents for customer approval
         \end{itemize}
      \end{cvitems}
    }

  \cventry
    {Software Engineer Intern}
    {}
    {}
    {Aug 2022 to Dec 2022}
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item Completed a 12 week full time equivalent internship as a required of Software Engineering Degree
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Overnight Crew Member} % Job title
    { McDonald's} % Organization
    {Williamtown, NSW} % Location
    {Feb 2015 to Jan 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Excellent multitasking with minimal crew members. Providing training and direction to new and existing crew members.}
        \item {Following safe work practices, such as wearing Personal Protective Equipment when cleaning high temperature oil vats.}
        \item {Performing full store cleaning to prepare to day shift.}
        \item {Efficient and hygienic food preparation for customers.}
        \item {Ensuring customer satisfaction by completing orders correctly and swiftly.}
        \item {Acquired excellent communication skills though customer interactions.}
      \end{cvitems}
    }

%---------------------------------------------------------
  % \cventry
  %   {Metal Working Work Experience} % Job title
  %   {Varley’s and Hyland Roofing} % Organization
  %   {Newcastle, NSW} % Location
  %   {Combined 35 hours} % Date(s)
  %   {
  %     \begin{cvitems} % Description(s) of tasks/responsibilities
  %       \item {Assisted with metal working jobs. Such as using sheet metal bender and welding equipment under supervision.}
  %       \item {Followed safe work practices by using appropriate Personal Protective Equipment.}
  %       \item {Followed instructions of supervising employees to ensure correct operation of equipment.}
  %     \end{cvitems}
  %   }

%---------------------------------------------------------
\end{cventries}
