%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

  %---------------------------------------------------------
  \cventry
  % , MongoDB
  {TypeScript ~·~ React ~·~ Express ~·~ Material UI ~·~ MongoDB ~·~ OpenSeadragon ~·~ Docker } % Tech
  {Capstone Project ~·~ Custom Web Based Microscope Slide Viewer } % Project type
  {The University of Newcastle} % Location (unneeded)
  {2023} % Date(s)
  {
    \begin{cvitems} % Description(s) of experience/contributions/knowledge
      \item {Completed as part of the final year project thesis for Bachelor of Software Engineering (Honours).}
      \item {Built for the University of Newcastle's LDTI (Learning and Teaching Digital Innovation) team to be used by Medical Students at the University of Newcastle.}
      \item {A successfully tested implementation which included features such as zooming, panning, navigation, annotations, and filtering options for high-resolution digital images was developed.}
      \item {Followed a hybrid waterfall and iterative development model. With regular client meetings and feedback.}
      \item {High resolution images are loaded from an AWS S3 bucket, metadata is stored in a MongoDB database and seamlessly displayed to the user using OpenSeadragon.}
    \end{cvitems}
  }

  % {
  % \begin{cvitems} % Description(s) of experience/contributions/knowledge
  %   \item {Implemented a prototype messaging system using Google Cloud Pub/Sub Topics.}
  %   \item {The Publisher was run in Google Cloud Run. The Subscriber was run in Google Cloud Functions.}
  %   \item {The Publisher continuously publishes messages to the Pub/Sub topic. The Subscriber then receives the message.}
  %   \item {The message is sent from the subscriber to a remote endpoint. This endpoint was built using Spring Boot, Thymeleaf and Bootstrap CSS}
  %   \item {The endpoint stores the messages and displays an automatically updated results table using JQuery}
  % \end{cvitems}
  % }

  % Project was completed as part of final year capstone thesis
  % Build for the University of Newcastle's LDTI (Learning and Teaching Digital Innovation) team to be used by Medical Students at the University of Newcastle.
  % Completed a successfully tested implementation which included features such as zooming, panning, navigation, annotations, and filtering options for high-resolution digital images.
  % Followed a hybrid waterfall and iterative development model. With regular client meetings and feedback.

  \cventry
  {Google Cloud ~·~ Java ~·~ Spring Boot ~·~ Thymeleaf ~·~ Bootstrap CSS ~·~ JQuery ~·~ Docker } % Tech
  {Cloud Pub/Sub Messaging Prototype with Cloud Endpoint} % Project type
  {The University of Newcastle} % Location (unneeded)
  {2022} % Date(s)
  {
    \begin{cvitems} % Description(s) of experience/contributions/knowledge
      \item {Implemented a prototype messaging system using Google Cloud Pub/Sub Topics.}
      \item {The Publisher was run in Google Cloud Run. The Subscriber was run in Google Cloud Functions.}
      \item {The Publisher continuously publishes messages to the Pub/Sub topic. The Subscriber then receives the message.}
      \item {The message is sent from the subscriber to a remote endpoint. This endpoint was built using Spring Boot, Thymeleaf and Bootstrap CSS}
      \item {The endpoint stores the messages and displays an automatically updated results table using JQuery}
    \end{cvitems}
  }

  \cventry
  {Java ~·~ LWJGL ~·~ OpenGL ~·~ GLSL} % Tech
  {3D OpenGL Game} % Project type
  {The University of Newcastle} % Location (unneeded)
  {2021} % Date(s)
  {
    \begin{cvitems} % Description(s) of experience/contributions/knowledge
      \item {Created a 3D OpenGL game from scratch using Java and LWJGL. Implemented GPU shaders with GLSL.}
      \item {Incorporated Phong shading for lighting, Basic GPU particle system with bill boarded textures.}
      \item {Also implemented Shadow maps with Depth Bias and Normal Offset to compensate for Peter Panning and Shadow acne.}
      \item {Included 3D camera movement and flight sim like model following camera.}
    \end{cvitems}
  }
  %---------------------------------------------------------
\end{cventries}